Hypertension and microbiome

### 2018-12-31 rrbiome.Rmd
eval FALSE

```{r alpha diversity scatterplot, fig.width=10, fig.height=4}
ggplot((dset.alpha %>%
        select(BL_AGE, BMI, SYSTM, DIASM, PULSEPRESSURE, MAP, SEX, diversities_shannon) %>%
        gather(Covariate, Value, -SEX, -diversities_shannon)), 
       aes(x=diversities_shannon, y=Value)) +
    facet_wrap(~Covariate, ncol=4, scales = "free") +
    geom_point(size=0.1, shape=1, aes(colour = SEX)) +
    geom_smooth(method=lm, se=TRUE, size=0.5, color = 'Black') +
    stat_poly_eq(formula = "y ~ x",
                 aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                 label.y = 0,
                 parse = TRUE,
                 size = 3) +   
    ylim(0, 200) +
    ggplot2::theme_minimal() 
```

@@

```{r lm model}
lm(MAP ~ diversities_shannon, data=dset.alpha) %>%
    summary(.) %>% coef %>% kable(., digits=4)
lm(MAP ~ BL_AGE + SEX + diversities_shannon, data=dset.alpha) %>%
    summary(.) %>% coef %>% kable(., digits=4)
lm(MAP ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + diversities_shannon, data=dset.alpha) %>%
    summary(.) %>% coef %>% kable(., digits=4)

@@

```{r vegdist}

@@

```{r beta hclust, fig.width = 5, fig.height = 4, dpi = 300}
gplots::heatmap.2(dist.matrix,
                  distfun = dist,
                  trace = "none",
                  hclustfun = hclust,
                  key.title = NA,
                  dendrogram = "column",
                  density.info = "none",
                  labRow = NA,
                  labCol = NA)
```

@@

```{r adonis1}
adonis(dist.matrix ~ MAP, 
       data = meta(pseq_filtered),
       permutations = 99)$aov.tab %>%
                            as.data.frame %>%
                            kable
```

```{r adonis2}
adonis(dist.matrix ~ BL_AGE + SEX + MAP,
       data = meta(pseq_filtered),
       permutations = 99)$aov.tab %>%
                            as.data.frame %>%
                            kable
```

```{r adonis3}
adonis(dist.matrix ~ MAP + BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + BP_TREAT,
       data = meta(pseq_filtered),
       permutations = 99)$aov.tab %>%
                            as.data.frame %>%
                            kable
```

@@

```{r pca}
pseq.clr <- microbiome::transform(pseq_filtered, "clr")
X <- as.matrix(t(abundances(pseq.clr)))
prcomp <- stats::prcomp(X)
```

```{r pca labels}
percentage <- round(prcomp$sdev/sum(prcomp$sdev) * 100, 2)
pca.labels <- paste0(colnames(prcomp$x), " (", paste0(as.character(percentage), "%", ")"))
```

```{r PCA plots categorical, fig.width = 10, fig.height = 10, dpi = 300}
ggplot((cbind(meta(pseq_filtered), prcomp$x[,1:2]) %>%
        select(PC1, PC2, BP_TREAT, CURR_SMOKE, DIAB, BL_USE_RX_C09, Q57X,
               BL_USE_RX_C03, BL_USE_RX_C07, BL_USE_RX_C08, HYPERTENSION, SEX) %>%
        gather(Covariate, Value, -PC1, -PC2)), 
       aes(x=PC1, y=PC2)) +
    facet_wrap(~Covariate, ncol=2, scales = "free") +
    geom_point(aes(color = Value), size = 0.5) +
    scale_color_brewer(palette="Dark2") +
    xlab(pca.labels[1]) +
    ylab(pca.labels[2]) +
    ggplot2::theme_minimal()

@@

```{r PCA plots continuous, fig.width = 10, fig.height = 10, dpi = 300}

@@

```{r prepare maaslin}

@@

```{r Reading maaslins output}

@@

```{r scatter plots}

@@

```{r maaslin scatter plot, fig.width = 10, fig.height = 20, dpi = 300}

>>>>

```{r alpha diversity scatterplot, fig.width=10, fig.height=4, eval = FALSE}
ggplot((dset.alpha %>%
        select(BL_AGE, BMI, SYSTM, DIASM, PULSEPRESSURE, MAP, SEX, diversities_shannon) %>%
        gather(Covariate, Value, -SEX, -diversities_shannon)), 
       aes(x=diversities_shannon, y=Value)) +
    facet_wrap(~Covariate, ncol=4, scales = "free") +
    geom_point(size=0.1, shape=1, aes(colour = SEX)) +
    geom_smooth(method=lm, se=TRUE, size=0.5, color = 'Black') +
    stat_poly_eq(formula = "y ~ x",
                 aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                 label.y = 0,
                 parse = TRUE,
                 size = 3) +   
    ylim(0, 200) +
    ggplot2::theme_minimal() 
```

@@

```{r lm model, eval = FALSE}
lm(MAP ~ diversities_shannon, data=dset.alpha) %>%
    summary(.) %>% coef %>% kable(., digits=4)
lm(MAP ~ BL_AGE + SEX + diversities_shannon, data=dset.alpha) %>%
    summary(.) %>% coef %>% kable(., digits=4)
lm(MAP ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + diversities_shannon, data=dset.alpha) %>%
    summary(.) %>% coef %>% kable(., digits=4)

@@

```{r vegdist, eval = FALSE}

@@

```{r beta hclust, fig.width = 5, fig.height = 4, dpi = 300, eval = FALSE}
gplots::heatmap.2(dist.matrix,
                  distfun = dist,
                  trace = "none",
                  hclustfun = hclust,
                  key.title = NA,
                  dendrogram = "column",
                  density.info = "none",
                  labRow = NA,
                  labCol = NA)
```

@@

```{r adonis1, eval = FALSE}
adonis(dist.matrix ~ MAP, 
       data = meta(pseq_filtered),
       permutations = 99)$aov.tab %>%
                            as.data.frame %>%
                            kable
```

```{r adonis2, eval = FALSE}
adonis(dist.matrix ~ BL_AGE + SEX + MAP,
       data = meta(pseq_filtered),
       permutations = 99)$aov.tab %>%
                            as.data.frame %>%
                            kable
```

```{r adonis3, eval = FALSE}
adonis(dist.matrix ~ MAP + BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + BP_TREAT,
       data = meta(pseq_filtered),
       permutations = 99)$aov.tab %>%
                            as.data.frame %>%
                            kable
```

@@

```{r pca, eval = FALSE}
pseq.clr <- microbiome::transform(pseq_filtered, "clr")
X <- as.matrix(t(abundances(pseq.clr)))
prcomp <- stats::prcomp(X)
```

```{r pca labels, eval = FALSE}
percentage <- round(prcomp$sdev/sum(prcomp$sdev) * 100, 2)
pca.labels <- paste0(colnames(prcomp$x), " (", paste0(as.character(percentage), "%", ")"))
```

```{r PCA plots categorical, fig.width = 10, fig.height = 10, dpi = 300, eval = FALSE}
ggplot((cbind(meta(pseq_filtered), prcomp$x[,1:2]) %>%
        select(PC1, PC2, BP_TREAT, CURR_SMOKE, DIAB, BL_USE_RX_C09, Q57X,
               BL_USE_RX_C03, BL_USE_RX_C07, BL_USE_RX_C08, HYPERTENSION, SEX) %>%
        gather(Covariate, Value, -PC1, -PC2)), 
       aes(x=PC1, y=PC2)) +
    facet_wrap(~Covariate, ncol=2, scales = "free") +
    geom_point(aes(color = Value), size = 0.5) +
    scale_color_brewer(palette="Dark2") +
    xlab(pca.labels[1]) +
    ylab(pca.labels[2]) +
    ggplot2::theme_minimal()

@@

```{r PCA plots continuous, fig.width = 10, fig.height = 10, dpi = 300,  eval = FALSE}

@@

```{r prepare maaslin, eval = FALSE}

@@

```{r Reading maaslins output, eval = FALSE}

@@

```{r scatter plots, eval = FALSE}

@@

```{r maaslin scatter plot, fig.width = 10, fig.height = 20, dpi = 300, eval = FALSE}
